Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-07-11 SupportingInformation.Rmd
NA error fixing

  return(list(tab_dbp=tab_dbp,
         cop_tab_dbp=cop_tab_dbp))
}
#-----------------------------
r_ple<-read.delim("./Data/Ceder_creek_e120/edited_ple120.txt")
r_pce<-read.delim("./Data/Ceder_creek_e120/edited_pce120.txt")

@@

<!--This chunk is for npa testing results of BMR dataset-->
```{r stat_BMR_graphic_approach, echo=F, results="hide", cache=T, cache.extra=list(seed,v_BMR,mtime("bivfunctionplot.R"),mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
source("bivfunctionplot.R")
set.seed(seed) 
# Now do NPA for v_BMR
source("bivfunctionplot.R")
stat_BMR_ga<-bivfunctionplot(v=v_BMR,resloc="./Results/BMR_results/",nametag="BMR_numbin_10",numbin = 10)
stat_BMR_ga_numbin5<-bivfunctionplot(v=v_BMR,resloc="./Results/BMR_results/",nametag="BMR_numbin_5",numbin = 5)
```

@@

for(i in 1:length(BivMS_res_cc)){
  BivMS_res_cc[[i]]<-OurBiCopSelect(u1=cop_HB_all_yr[[i]]$avg.H,u2=cop_HB_all_yr[[i]]$avg.Biomass,
                                    families=c(1,3:10,13:14,16:20),
                                    level=0.05,AICBIC="AIC",
                                    numBSsmall=100,pthresh=0.2,numBSlarge=1000,gofnormal=F,status=F)
}
saveRDS(BivMS_res_cc,file="./Results/Ceder_creek_results/BivMS_res_cc.RDS")
```

>>>>

  return(list(tab_dbp=tab_dbp,
         cop_tab_dbp=cop_tab_dbp))
}
#-----------------------------
r_ple<-read.delim("./Data/Ceder_creek_e120/edited_ple120.txt")
names(r_ple)[36]<-"Biomass"

r_pce<-read.delim("./Data/Ceder_creek_e120/edited_pce120.txt")

@@

<!--This chunk is for npa testing results of BMR dataset-->
```{r stat_BMR_graphic_approach, echo=F, results="hide", cache=T, cache.extra=list(seed,v_BMR,mtime("bivfunctionplot.R"),mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
source("bivfunctionplot.R")
set.seed(seed) 
# Now do NPA for v_BMR
stat_BMR_ga<-bivfunctionplot(v=v_BMR,resloc="./Results/BMR_results/",nametag="BMR_numbin_10",numbin = 10)
stat_BMR_ga_numbin5<-bivfunctionplot(v=v_BMR,resloc="./Results/BMR_results/",nametag="BMR_numbin_5",numbin = 5)
```

@@

for(i in 1:length(BivMS_res_cc)){
  BivMS_res_cc[[i]]<-OurBiCopSelect(u1=cop_HB_all_yr[[i]]$avg.H,u2=cop_HB_all_yr[[i]]$avg.Biomass,
                                    families=c(1,3:10,13:14,16:20),
                                    level=0.05,AICBIC="AIC",
                                    numBSsmall=100,pthresh=0.2,numBSlarge=1000,gofnormal=F,status=F)
}
saveRDS(BivMS_res_cc,file="./Results/Ceder_creek_results/BivMS_res_cc.RDS")
BivMS_res_cc<-readRDS("./Results/Ceder_creek_results/BivMS_res_cc.RDS")
```
